---
title: "Lab 03"
author: "YOUR NAME HERE"
date: "XX/XX/20XX"
output: 
  html_document:
    toc: TRUE
---
#Chunk 1: Load libraries and Data
  1.1) Load the packages `ggplot2`, `tidyverse` and `datasets` 
	1.2) Load the dataset `sleep` 
	1.3) Using a comment describe the structure `str()` of the ‘sleep’ dataset

```{r}
?library
library (tidyverse)
?data
?str
```

#Chunk 2: One Dimmensional Data Visualization- Histograms
  2.1) Using `ggplot`, `geom_histogram()`, `gg_title` plot a histogram of the sleep dataset’s variable “extra” using the default bins setting and title each plot based on the number of bins displayed.
  2.2) Now modify the `bins` argument from 30 (default) and create new plots, (change 
the title to reflect the number of bins being displayed) 
  2.3) Using a comment describe what happens when you change the bin size? 

```{r}
?ggplot()
?geom_histogram()
?ggtitle()

```

#Chunk 3: One Dimmensional Data Visualization- Density Plots
	3.1) Create a density plot for the variable “extra” in the “sleep” dataset	
	3.2) modify the x axis to range from -10 to 10
	3.3) Create a new density plot but color the density plot by “group” with a 50% 
transparency 

```{r}
?ggplot
?geom_denisty

```

#Chunk 4: Generate a Random Normal Distribution
  4.1 Create an object called “extra” of a normal distribution with a 20 observations a 
mean of 0 and a standard deviation of 1. 

	4.2. Convert norm from a list to a data.frame (?as.data.frame)

  4.3 Plot it as a density plot: `geom_density()`

  4.4 Change the number of observations to 10 and plot it as a density plot. Using a comment, how does the distribution change? 

  4.5. Change the number of observations to 100 and plot it as a density plot. Using a comment, how does the distribution change? 

  4.6 Use `shapiro.test` to test for normality in this distribution? What do the results suggest? Are the data normally distributed? 

```{r}
set.seed(198)
?rnorm
?as.data.frame

```

#Chunk 5: Data Merging and plotting
	5.1) Create a new object called “norm.table”; Add two columns to the `extra` dataframe and name them “group” and “ID” fill the cells with the value “RANDOM”

	5.2) Bind the ‘norm.table’ object with the ‘sleep’ data in a new object called ‘new.df’(?rbind)

	5.3) Plot the ‘new.df’ object as a density plot, colored by “group” with a 50% transparency 

	5.4) Use the `filter` function to select only the observations for group 1; are these data normally distributed? 

	5.5) Use the `filter` function to select only the observations for group 2; are these data normally distributed? 

```{r}
?add_column
?rbind

```

#Chunk 6: Checking for `kurtosis` and `skewness`
	6.1) load the library `(e1071)` which has the functions `kurtosis` and `skewness`? What are the arguments in these functions? 

	6.2) Compare the Kurtosis and skewness between the random normal distribution you generated and group 1 and group 2. 
	  * For kurtosis and skewness set the type=2 for unbiased, normal data. 

```{r}

```

#Chunk 7: Fancy Plotting
Do any five of these things to the version of the plot completed in chunk 5:
	
	* change the default color of the plot to different color using  ‘scale_fill_manual’
	
	* change the x label to “Effect on hours of sleep”
	
	* change the background theme to black and white ‘theme_bw()’
	
	* add a vertical line at the mean value ‘geom_vline()’
	
	* change the label on the color key ‘labs’
	
	* change the position of the key from the right to the top or bottom 
	
	* add a title to the plot ‘ggtitle’
	
	* annotate the plot with some text (e.g. describing the vertical line) ‘annotate’
	
	* change the figure size to 4 in X 6 in (markdown chunk modification)
	
	* change the output resolution of the figure to 400 dpi (markdown chunk modification)

```{r}

```
