---
title: "Lab3_04_10_18"
author: "Del Toro"
date: "4/10/2018"
output: word_document
---
Load libraries, data and set a working directory 
```{r}
#Setwd 
setwd("/Users/israel/Desktop/Bio170_Spring_18/Lab03")
#laod data 
df<-read.csv ("Fitbit_lab3.csv")
#load libraries 
library (ggplot2)
library (dplyr)
```

Create a random distribution- binomial 
```{r}
Binom<-rbinom(size=4, n=100, .25)
Binom<-as.data.frame (Binom)
str (Binom)
summary (Binom)

Binom2<-rbinom(size=4, n=100, .75)
Binom2<-as.data.frame (Binom2)
str (Binom2)
summary (Binom2)

```

Plot the binomial distribution in ggplot2 as a density plot
```{r}
ggplot (Binom, aes (Binom)) + geom_density() + xlim (0,4)
ggplot (Binom2, aes (Binom2)) + geom_density()+ xlim (0,4)
```

Create a normal distribution- Gaussian 
```{r}
Normal1<- rnorm(n=100, mean = 170, sd = 5); Normal1<-as.data.frame(Normal1)
Normal2<- rnorm(n=100, mean = 160, sd = 3); Normal2<-as.data.frame(Normal2)

```

Plot the gaussian distributions in ggplot2
```{r}
ggplot (Normal1, aes (Normal1)) + geom_histogram(bins=50) + xlim (150, 200)
ggplot (Normal2, aes (Normal2)) + geom_histogram(bins=25)+ xlim (150, 200)
```

Working with fitbit data: 
Plot the distributions of height by gender as a density plot 
```{r}
ggplot (df, aes (x=Height, color=Gender, fill=Gender))  + geom_density(alpha=0.5)
```
Plot the distributions of weight by gender as a histogram plot 
```{r}
ggplot (df, aes (Weight, color=Gender)) + geom_histogram(bins=10)
```

Chunk 9: Summarize the data for height
```{r}
df %>%
  group_by(Gender) %>%
  summarise(mean = mean(Height), n = n(), sd = sd(Height))
```
