---
title: "Lab 2- Intro to R Markdown and Data"
author: "YOUR NAME HERE"
date: "X/XX/20XX"
output: 
  html_document:
    toc: TRUE
---
#Chunk 1: Load Libraries 
  1.1) Load ggplot2 and datasets libraries
  1.2) c.	Using a #; comment on two different arguments of the function `library`
```{r}
?library

```

#Chunk 2: Load Data
  2.1) Load the "InsectSprays" dataset
  
```{r}
?data

```

#Chunk 3: Data Exploring 
  3.1) Explore the structure of the data you just loaded using the functions `head()`, `str()` and `summary ()`, close the third chunk 
```{r}
?str
?head
?tail
?summary
```

#Chunk 4:My first Boxplot: ggplot2
  4.1) build your first ggplot using the functions `ggplot` and `geom_boxplot` using the `InsectSprays` dataset
  4.2) Decide and describe what variables go on the x-axis and what variables go on the y axis 
  4.3) Using a comment # describe the plot you see. What do the different lines on the boxplot mean? 
```{r}
?ggplot 
?geom_boxplot

```

#Chunk 5: Iris and violin plot 
  5.1) In this chunk load the dataset `iris`
  5.2) Create a violin plot for “Sepal.Length” where each species is colored differently, and the color fill is 50% transparent. 
  5.3)	Change the y axis label from “Sepal.Length to “Sepal Length (mm)” 
  5.4)	Close the chunk 

```{r}
?iris

```

### Knit and Submit 